---
title: "Gapminder Analysis"
author: "Rena"
date: "2024-02-07"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reading in gapminder data

```{r reading_in_data}
gapminder_df <- read.csv("data/gapminder_data.csv")
```

# Playing with Rmd files

## A smaller header

### An even smaller header

#### An even smaller header

-   list item 1

-   list item 2

-   list item 1

-   list item 2

1.  Number one
2.  Number two
    -   Under number two
3.  Number three

We can make text **bold** or *italic*. We can also insert greek letters like $\mu$. We can make [hyperlinks.](https://pad.carpentries.org/Spring2024-BIOMI6300)

# Calculating summary statistics

```{r calculating_median_pop, echo = FALSE}
med_pop = median(gapminder_df$pop)
num_obs = nrow(gapminder_df)
```

Over `r num_obs` observations, the median population is `r round(med_pop/(10^6),3)` million.

# Plotting life expectancy over years

```{r line_graph, warning= FALSE}
library(ggplot2)
ggplot(data = gapminder_df, aes(year, lifeExp, group = country, color = continent)) + 
  geom_line() + 
  scale_y_log10() + 
  theme_light() + 
  scale_x_continuous(limits = c(1997,2007))
```

# Plotting population distribution

```{r histogram, message=FALSE, warning= FALSE, fig.width= 10}
ggplot(gapminder_df, aes(pop)) +
  geom_histogram() + 
  scale_y_log10()
```

# Visual mode - tables

| Col1          | Col2 | Col3 |
|---------------|------|------|
| my stuff here |      |      |
|               |      |      |
|               |      |      |

Adding new lines for git 
